%-------------------------
% Resume in Latex
% Author : Shubhi Rani
% License : MIT
%------------------------

\documentclass[letterpaper,10.8pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{bibentry}
\usepackage{natbib}

\pagestyle{fancy}
\lhead{Zehan Yang}
\rhead{Resume}
\AtBeginDocument{\thispagestyle{empty}}
\cfoot{\thepage}



\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
	\vspace{-3pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
	\item\small{
		\textbf{#1}{: #2 \vspace{-2pt}}
	}
}

\newcommand{\resumeItemWithoutTitle}[1]{
	\item\small{
		{\vspace{-2pt}}
	}
}

\newcommand{\resumeSubheading}[4]{
	\vspace{-1pt}\item
	\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{\small#3} & \textit{\small #4} \\
	\end{tabular*}\vspace{-5pt}
}




\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=* ]}
	\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
	\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


      \begin{document}
	\cfoot{\thepage}
      % ----------HEADING-----------------
      \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
        \textbf{{\LARGE Zehan Yang}}&\\
        \href{https://github.com/YEnthalpy}{Github: https://github.com/YEnthalpy}&
        \href{zehan.yang@uconn.edu}{zehan.yang@uconn.edu}\\
        \href{https://www.linkedin.com/in/Zehan}{LinkedIn:
        https://www.linkedin.com/in/Zehan} & 860-634-0053 \\
      \end{tabular*}


	   \section{Qualification}
	   \begin{description}[font=$\bullet$]
	   	    \item Strong background using R, SAS and Python for research and projects.
	   	    \vspace{-5pt}
	   	    \item Sufficient experience in dealing with medical data.
	   	    \vspace{-5pt}
	   	    \item Proficient in statistical modeling using general linear model.
	   	    \vspace{-5pt}
	   	    \item Proven ability to identify, analyze, and solve problems.
	   	    \vspace{-5pt}
	   	    \item Worked both as a member and independently.
	   \end{description}
      % -----------EDUCATION-----------------
      \section{Education}
      \resumeSubHeadingListStart \resumeSubheading {University of
        Connecticut}{Storrs, CT, USA} {Ph.D. in Statistics; GPA: 3.93/4.3}{Aug 2023(Expected)}
        \vspace{3pt}

      Relevant course: Statistical Computing, Multivariate Statistics,
      Design of Experiments, Applied Statistics, Mathematical
      Statistics, Linear Statistical Models,
      Statistical Inference, Survival Analysis.\\
      Research Interest: Optimal Subsampling for Big Survival Data.

      \resumeSubheading {Xi'an Jiaotong University}{Xi'an, China}
      {Bachelor of Computational Mathematics; GPA: 3.43/4.3}{May 2018} \resumeSubHeadingListEnd

	%
      % --------PROGRAMMING SKILLS------------
      \section{Skills Summary}
      \resumeSubHeadingListStart \resumeSubItem{Languages}{R, SAS,
        C++, Matlab, Python} \resumeSubItem{Tools}{LaTex, Git, HPC Cluster, Slurm
        Workload Manager} \resumeSubHeadingListEnd



      % -----------EXPERIENCE-----------------
      \section{Experience}
      \resumeSubHeadingListStart
      \resumeSubheading {University of
        Connecticut}{Storrs, CT, USA} {Research Assistant - Prof. Jun Yan
        \& HaiYing Wang }{April 2020 - Current}
    \resumeItemListStart
      \resumeItem{Optimal Subsampling of Parametric Accelerate Failure
        Time (AFT) model for Big Survival Data}{}
      \begin{description}[font=$\bullet$]
      \item {Proved the asymptotic properties of the resultant
          estimator in the general subsampling approach.}
      \item {Proposed optimal subsampling probabilities based on
          A-optimality and L-optimality from the optimal design of
          experiment. }
      \item {Developed the two-step algorithm to get the resultant
          estimator using the optimal subsampling probabilities.}
      \item {Proved the asymptotic properties for the estimator
          derived by the two-step algorithm and propose the formula to
          estimate the variance and covariance matrix.}
      \item {Applied the simulation and the real data analysis based
          on parametric Weibull AFT model.}
      \end{description}
      \resumeItem{Optimal Subsampling of Semi-Parametric Accelerate
        Failure Time model for Big Survival Data}{}
      \begin{description}[font=$\bullet$]
      \item {Proposed a general estimating function for
          semi-parametric AFT model based on the least-squares
          approach .}
      \item {Used resampling method to construct a sandwich estimator
          for the variance-covariance matrix.}
      \item {Constructed A-optimal subsampling probabilities by the
          slope matrix that was the `bread` part of the sandwich
          estimator. }
      \item {Developed the two-step algorithm and the iterative
          algorithm to get the resultant estimator using the optimal
          subsampling probabilities.}
      \item {Compared the computational and estimation efficiency for
          two algorithms.}
      \item {Applied the simulation based on different error
          distributions. Finished the real data analysis based on a big
          lymphoma data.}
      \end{description}
      \resumeItemListEnd


    \resumeSubheading {University of Connecticut, Health
      Center}{Farmington, CT, USA} {Research Assistant - Prof. Helen(Zhao)
      Wu }{Sep 2021 - Current}
  \resumeItemListStart
  \resumeItem{Impact
      of Mental Disorder and Drug Addiction on Adult Bio-markers Among
      Low-income Women after Hurricane Ike}{}
    \begin{description}[font=$\bullet$]
    \item {Cleaned the Hurricane Ike data for 1000 observations.}
    \item {Selected patients who had bio-marker testing results before
        and after Hurricane Ike.}
    \item {Used an ANOVA model to investigate the influence of age,
        ethnicity, marital status, employment status and annual income
        on the changes in biomarkers. }
    \item {Implemented a mixed ANOVA model to detect if patients'
        bio-markers, such as `IL6`, `Cortisone`, `DHEAS`, changed
        after experiencing Hurricane Ike for different kinds of drug
        users and mentally disordered patients.}
    \end{description}
    \resumeItem{Multiple Consulting projects for medical researchers
      and medical doctors}{}
    \begin{description}[font=$\bullet$]
    \item {Applied a logistic regression to analyze the relationship
        between breast cancer biopsy status and patients' personal
        information based on breast cancer data in Sudan.}
    \item {Analyzed Medication Data for diabetics to evaluate if the
        CPAP machine helped patients control their A1C score.}
    \item {Applied Beta regression models to analyze the National Health Service (NHS)
    Survey data.}
    \end{description}
    \resumeItemListEnd

    \resumeSubheading {University of Connecticut}{Storrs, CT, USA}{Independent Teaching
    Assistant}{Sep 2021 -  Current}
    \resumeItemListStart
    \resumeItem{STAT 3375Q Introduction to
    	Mathematical Statistics I Teaching Assistant}{\\Lead discussion
    	sessions and hold office hours weekly.}
    \resumeItem{STAT 3445
    	Introduction to Mathematical Statistics II Teaching
    	Assistant}{\\Lead discussion sessions and hold an office hour
    	weekly.}
    \resumeItem{STAT 1000Q/1100Q Introduction to
    	Statistics Teaching Assistant}{\\Teaching students how to use
    	Minitab during the discussion and grading their Minitab
    	assignments weekly. }
    \resumeItemListEnd
	\resumeSubHeadingListEnd

	\section{Professional Associations}
    \begin{description}[font=$\bullet$]
    	\item {Membership of American Statistical Association}
    	\vspace{-5pt}
    	\item {Membership of New England Statistical Society}
    \end{description}

    \section{Presentations}
     \begin{description}[font=$\bullet$]
    	\item Optimal Subsampling for Parametric Accelerated Failure Time
    	Models with Massive Survival Data. \textit{2022 Joint Statistical Meetings},
    	Washington D.C., August 6 - August 11, 2022.
    \end{description}

    % -----------PROJECTS-----------------
    \section{Honors and Awards}
    \begin{description}[font=$\bullet$]
    \item {The 2022 LiDS Student Paper Award by the American
        Statistical Association.}
    \end{description}
    % -------------------------------------------

    \section{Publications}
    \begin{description}[font=$\bullet$]
    	\item Yang, Z., H. Wang, and J. Yan (2022). Optimal Subsampling for Parametric
    	Accelerated Failure Time Models with Massive Survival Data. \textit{Statistics in
    	Medicine 41(27)}, 5421–5431.
    \end{description}

  \end{document}
